%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}
%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{GIS Engineer} % Job title
{RMSI} % Organization
{UK} % Location
{Nov. 2025 --- Present} % Date(s)
{
\begin{cvitems}
\item {Process and manage large-scale spatial datasets from local authorities and government sources.}
\item {Design, develop, and maintain production-ready FME Workbenches to support the spatial charge digitisation and transformation, attribute mapping and schema alignment to data standards.}
\item {Perform advanced spatial operations, spatial joins, overlays, snapping, buffering and topology validation.}
\item {Perform quality assurance, and topological checks to ensure accuracy and consistency.}
\item {Contribute to digitisation workflows, aligning with data specifications and project standards.}
\item {Collaborate with the data and QA teams to resolve mapping or attribute discrepancies.}
\item {Prepare maps, reports, and spatial deliverables as required by project managers.}
\item {Managed and maintained web GIS content, including layers, maps, and applications within ArcGIS Enterprise, ensuring data integrity and accessibility.}
\vspace{0.8em}
\end{cvitems}
}
%---------------------------------------------------------
\cventry
{GIS Technician} % Job title
{Cyient Europe Ltd} % Organization
{UK} % Location
{Nov. 2023 --- Nov. 2025} % Date(s)
{
\begin{cvitems}
\item {Produced geospatial databases with more than 96\% accuracy to support project delivery.}
\item {Managed thousands of utility records in accordance with the land and asset requirements of the UK.}
\item {Updated geospatial data using aerial photography, remote sensing imagery, and Ordnance Survey datasets to reflect real-world changes.}
\item {Identified and resolved technical mapping errors, which resulted in about 20\% less rework.}
\item {Actively contributed to weekly meetings, providing insights and technical recommendations to cross-functional teams.}
\item {Used SQL for data management and technical reports.}
\item {Performed georeferencing on historical and current maps to align spatial data with real-world coordinates.}
\vspace{0.8em}
\end{cvitems}
}
%---------------------------------------------------------
\cventry
{GIS Analyst} % Job title
{Centre for Education, Culture and Research Institute} % Organization
{Iran} % Location
{Sep. 2019 --- Aug. 2023} % Date(s)
{
\begin{cvitems}
\item {Enhanced data management by creating comprehensive metadata for 100+ GIS projects, ensuring consistency, accessibility, and improved data quality across the organisation.}
\item {Collected data using Field Maps and Survey123 for producing detailed technical maps in GIS applications and spatial analysis projects.}
\item {Developed spatial models using Esri software for supporting environmental, infrastructure and climate change projects.}
\item {Improved analytical reliability by conducting decision-making analysis using raster and RS imagery, including classification, and change detection.}
\item {Cleaned and processed large geospatial datasets using Python, reducing manual data preparation time by 40\% through automation.}
\item {Developed and deployed interactive web GIS applications using Experience Builder and ArcGIS Online to support data visualisation, stakeholder engagement, and decision-making.}
\item {Executed advanced SQL queries and managed spatial datasets using PostgreSQL/PostGIS, increasing data retrieval and processing performance by 25\%.}
\item {Created 3D maps using R programming, leading to clearer and more effective presentations for stakeholders.}
\item {Performed site suitability and geospatial analysis that informed location decisions for multiple development projects, increasing project efficiency and reducing evaluation time.}
\vspace{0.8em}
\end{cvitems}
}
%---------------------------------------------------------
\cventry
{Research Assistant} % Job title
{TheUniversity of Guilan} % Organization
{Iran} % Location
{Jan. 2016 --- Sep. 2018} % Date(s)
{
\begin{cvitems}
\item {Supported methodology and hypothesis development.}
\item {Conducted interviews and gathered data from a variety of communities.}
\item {Prepared thematic maps using advanced cartographic techniques with Geographic Information System.}
\end{cvitems}
}
%---------------------------------------------------------
\end{cventries}
% \clearpage