%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications and Research}

%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\vspace{0.4em}

{\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text}
\begin{cvitems}

\item {Majid Yasouri, Mehdi Khayyati, and \textbf{Fatemeh Momeni Taromsari}. Prioritization of factors affecting the enhancement of regional economic competitiveness: A case study of Rudbar County. \textit{Journal of Spatial Economics and Rural Development}, 12(2):223--248, 2023.}

\item {Mohammad Ali Rahimipour Sheikhani Nejad, Habib Mahmoodi Chenari, Farzaneh Nasiri Jan Agha, \textbf{Fatemeh Momeni Taromsari}, Seyyedeh Fatemeh Emami, and Zahra Jensi. Land use planning to determine the optimal spaces for developing sustainable rural employment in East Guilan. \textit{Journal of Sustainable Rural Development}, 7(1):31--44, 2023.}

\item {Habib Mahmoodi Chenari, Mohammad Ali Rahimi Poursheikhani Nejad, \textbf{Fatemeh Momeni Taromsari}, Farzaneh Nasiri Jan Agha, and Zahra Jensi. Development of sustainable rural employment by creating skills houses based on the scenario method: Case study: Rural areas of East Guilan. \textit{Journal of Rural Research}, 12(1):174--193, 2021.}

\item {Habib Mahmoodi Chenari, Mohammad Ali Rahimipour Sheikhani Nejad, \textbf{Fatemeh Momeni Taromsari}, Farzaneh Nasiri, and Zahra Jensi. Analysis of importance--performance indicators of sustainable rural employment based on the natural environment: Case study: Rural area of East Guilan. \textit{Geographical Studies of Coastal Areas Journal}, 1(3):119--145, 2021.}

\end{cvitems}
}

\vspace{1.0em}